\documentclass[12pt]{article}
\usepackage[left=1in, right=1in]{geometry}

\usepackage{url}

%\usepackage{arydshln}

\usepackage{graphicx}

\usepackage{color}
\definecolor{light-gray}{gray}{0.30}

\usepackage{listings}
\lstset{
	frame=leftline,
	frameround=ttff,
	numbers=left,
	language=C++,
	showstringspaces=False,
	extendedchars=False,
	numberstyle=\footnotesize,
	basicstyle=\small\ttfamily,
	commentstyle=\color{light-gray}\slshape,
	belowskip=1.5em,
	aboveskip=1.5em,
	fontadjust,
	tabsize=4,		%added for proper tab alligning
	xleftmargin=0cm,
	xrightmargin=0cm
}


\newcommand{\desc}[1]{\textit{#1} \vspace{1em}}

\title{\itshape Exercises week 2}

\author{
	Klaas Isaac Bijlsma \\ s2394480
	\and
	David Vroom \\ s2309939
}

\date{\today}

\begin{document}
\maketitle

\section*{Exercise 11}
\desc{Learn to appreciate catching references when throwing exceptions}

A simple class \texttt{Object} is made. It has a data member \texttt{d\_name} that stores an internal name. If an object is made via the copy constructor, 'copy' is added to this internal name. The constructor, copy constructor and destructor print what they did together with the internal name. A function \texttt{hello()} is added that says hello and prints the internal name. 
\lstinputlisting[title=\texttt{object/object.h}]{../ex11/object/object.h}
\lstinputlisting[title=\texttt{object/object.ih}]{../ex11/object/object.ih}
\lstinputlisting[title=\texttt{object/destructor.cc}]{../ex11/object/destructor.cc}
\lstinputlisting[title=\texttt{object/hello.cc}]{../ex11/object/hello.cc}
\lstinputlisting[title=\texttt{object/object1.cc}]{../ex11/object/object1.cc}
\lstinputlisting[title=\texttt{object/object2.cc}]{../ex11/object/object2.cc}

\vspace{0.5cm}
Below a main function (\texttt{main1.cc}) is shown, in which within a try block, an object of the class \texttt{Object} is made. This object is then thrown. The exception handler catches an object of the class \texttt{Object} (by value). The output of the program is given below the code of main1. We see that the object is properly constructed and says hello. Then when it is thrown, first a copy is made and the original object is destructed. The copy is passed to the exception handler. Here an additional copy is made, because it receives the object by value. Therefore, within the exception handler, the copy of the copy of the object says hello.
\lstinputlisting[title=\texttt{main1.cc}]{../ex11/main1.cc}
\lstinputlisting[title=\texttt{Output of main1.cc},language=bash, numbers=none]{../ex11/outputMain1.txt}

\vspace{0.5cm}
The following main function (\texttt{main2.cc}) does the same as the previous, except that the exception handler catches \emph{a reference} to an object of the class \texttt{Object}. From the output we see that no second copy is made. This is more efficient and therefore exception handlers should catch references to objects. 
\lstinputlisting[title=\texttt{main2.cc}]{../ex11/main2.cc}
\lstinputlisting[title=\texttt{Output of main2.cc},language=bash, numbers=none]{../ex11/outputMain2.txt}

\vspace{0.5cm}
In the previous two programs, we saw that a copy of the object is thrown. This is because the original object is a local object that only lives inside the try block. The same is true when a reference to an object is thrown, as can be seen from the output that the following code produces:
\lstinputlisting[title=\texttt{main3.cc}]{../ex11/main3.cc}
\lstinputlisting[title=\texttt{Output of main3.cc},language=bash, numbers=none]{../ex11/outputMain3.txt}

\vspace{0.5cm}
The following main function (\texttt{main4.cc}) has two exception levels. In the inner level, an object of the class \texttt{Object} is thrown and caught as a reference. Then it is rethrown to a more shallow level where it is again caught as a reference. From the shown output, we conclude that '\texttt{throw;}' results in throwing the currently available exception and not a copy of that exception.
\lstinputlisting[title=\texttt{main4.cc}]{../ex11/main4.cc}
\lstinputlisting[title=\texttt{Output of main4.cc},language=bash, numbers=none]{../ex11/outputMain4.txt}


\clearpage
\section*{Exercise 12}
\desc{Study the way \texttt{delete[]} works}

We used the following code,

\lstinputlisting[title=\texttt{maxfour/maxfour.h}]{../ex12/maxfour/maxfour.h}
\lstinputlisting[title=\texttt{maxfour/maxfour.ih}]{../ex12/maxfour/maxfour.ih}
\lstinputlisting[title=\texttt{maxfour/data.cc}]{../ex12/maxfour/data.cc}
\lstinputlisting[title=\texttt{maxfour/destructor.cc}]{../ex12/maxfour/destructor.cc}
\lstinputlisting[title=\texttt{main.ih}]{../ex12/main.ih}
\lstinputlisting[title=\texttt{main.cc}]{../ex12/main.cc}
\lstinputlisting[title=\texttt{Output of main.cc},language=bash, numbers=none]{../ex12/outputMain.txt}

\textbf{Explain why the solution is so simple}\\
The solution is so simple because when an exception is thrown during the construction of an array of 10 Maxfour objects, stack unwinding will destroy the already allocated objects. No explicit call of the destructor is needed. Furthermore we do not need to keep track of the already allocated objects. 

\clearpage
\section*{Exercise 13}
\desc{Learn to create an exception safe class}

We modified the following code of the matrix solution,
\lstinputlisting[title=\texttt{main.cc}]{../ex13/main1.cc}
\lstinputlisting[title=\texttt{matrix/matrix.h}]{../ex13/matrix/matrix.h}
\lstinputlisting[title=\texttt{matrix/matrix.ih}]{../ex13/matrix/matrix.ih}
\lstinputlisting[title=\texttt{matrix/at.cc}]{../ex13/matrix/at.cc}
\lstinputlisting[title=\texttt{matrix/identity.cc}]{../ex13/matrix/identity.cc}
\lstinputlisting[title=\texttt{matrix/matrix1.cc}]{../ex13/matrix/matrix1.cc}
\lstinputlisting[title=\texttt{matrix/matrix2.cc}]{../ex13/matrix/matrix2.cc}
\lstinputlisting[title=\texttt{matrix/matrix4.cc}]{../ex13/matrix/matrix4.cc}
\lstinputlisting[title=\texttt{matrix/operatorassign1.cc}]{../ex13/matrix/operatorassign1.cc}
\lstinputlisting[title=\texttt{matrix/operatorassign2.cc}]{../ex13/matrix/operatorassign2.cc}
\lstinputlisting[title=\texttt{matrix/swap.cc}]{../ex13/matrix/swap.cc}
\lstinputlisting[title=\texttt{matrix/tr.cc}]{../ex13/matrix/tr.cc}
\lstinputlisting[title=\texttt{matrix/transpose.cc}]{../ex13/matrix/transpose.cc}


\clearpage
\section*{Exercise 16}
\desc{Learn how to end a program safely}

\textbf{How do you end a program in such a situation?}

In main wordt een object geconstruct en een functie aangeroepen die throwt. Deze functie doet vervolgens hetzelfde net als de functie daar weer in. In het diepste nested level wordt de throw operator daadwerkelijk aangeroepen, de exception gethrowd en vervolgens gerethrowd. Zodra de exception gethrowd wordt en de exception het try-block verlaat, wordt de destructor aangeroepen, net als in de levels daarboven.
Op deze manier worden alle constructed objects netjes vernietigd.\\

De volgende code verduidelijkt dit,

\lstinputlisting[title=\texttt{demo/demo.h}]{../ex16/demo/demo.h}
\lstinputlisting[title=\texttt{demo/demo.ih}]{../ex16/demo/demo.ih}
\lstinputlisting[title=\texttt{demo/demo.cc}]{../ex16/demo/demo.cc}
\lstinputlisting[title=\texttt{demo/destructor.cc}]{../ex16/demo/destructor.cc}
\lstinputlisting[title=\texttt{main.ih}]{../ex16/main.ih}
\lstinputlisting[title=\texttt{main.cc}]{../ex16/main.cc}
\lstinputlisting[title=\texttt{function1.cc}]{../ex16/function1.cc}
\lstinputlisting[title=\texttt{function2.cc}]{../ex16/function2.cc}
\lstinputlisting[title=\texttt{function3.cc}]{../ex16/function3.cc}

\clearpage
\section*{Exercise 17}
\desc{Learn to understand how throw lists and noexept work}

A small class \texttt{ShowExcepts} is made. It has a constructor and two functions \texttt{asAthrowList()} and \texttt{asNoexcept()}, that behave as if \texttt{throw (int, std::string)} or the keyword \texttt{noexcept} is specified, respectively, while this is not actually specified. When this would be speciefied, the compiler generates additional code, and this code is now already provided by us, thus simualiting the use of the specifications. 
The two member functions call a function \texttt{test()}, which prints that it is called and throws an exception (below the code, the output is discussed when this exception is an int or a double). 


\lstinputlisting[title=\texttt{showexcepts/showexcepts.h}]{../ex17/showexcepts/showexcepts.h}
\lstinputlisting[title=\texttt{showexcepts/showexcepts.ih}]{../ex17/showexcepts/showexcepts.ih}
\lstinputlisting[title=\texttt{showexcepts/showexcepts1.cc}]{../ex17/showexcepts/showexcepts1.cc}
\lstinputlisting[title=\texttt{showexcepts/asathrowlist.cc}]{../ex17/showexcepts/asathrowlist.cc}
\lstinputlisting[title=\texttt{showexcepts/asnoexcept.cc}]{../ex17/showexcepts/asnoexcept.cc}
\lstinputlisting[title=\texttt{main.ih}]{../ex17/main.ih}
\lstinputlisting[title=\texttt{main.cc}]{../ex17/main.cc}
\lstinputlisting[title=\texttt{test.cc}]{../ex17/test.cc}

If \texttt{test()} throws a double (e.g. 1.5), the output shown below is produced. In \texttt{asathrowlist}, the double is not caught by the int or string catcher, but by the catch-all, throwing a \texttt{bad\_exception}. 

In the second try block, \texttt{asnoexcept} is called, which calls \texttt{std::terminate()}, terminating the program. Therefore, the cout statement in \texttt{main}'s final catch clause is not reached. 

\lstinputlisting[title={Output when \texttt{test()} throws a double (1.5)},language=bash, numbers=none]{../ex17/outputDouble.txt}

If \texttt{test()} throws an int (e.g. 1), the output shown below is produced. In \texttt{asathrowlist}, the int is caught by the int catcher, and then rethrown. In \texttt{main}, it is then caught by the catch-all handler, giving the shown output. 

\lstinputlisting[title={Output when \texttt{test()} throws an int (1)},language=bash, numbers=none]{../ex17/outputInt.txt}



\clearpage
\section*{Exercise 18}
\desc{Learn to identify points where exceptions may be thrown}
See 10.10 Annotations ;-)

\clearpage

\end{document}
